Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-03-29 RMS/submission.tex
first version done for major revision
modified version wrt Zhou Min's comments

We also randomly generate test scenarios under the above setting to
exam the efficiency of our approach for verifying the schedulability.
Among the $50$ generated test scenarios with $5$ tasks, we find that
the execution time of the model checking command for each scenario
varies from about $300ms$ up to a timeout, which is set to $90$
minutes. This is because the efficiency of model checking depends on
the scale of the state space. And the scale is further positively
correlated with $mn$, where $m$ is the upper bound of $timer$ and $n$
is the number of periodic tasks. By the generated test scenarios, it
turns out that the model checking command for schedulability in our
model is able to handle scenarios, where $mn$ is up to about $10^6$,
in an acceptable period of time say $90$ minutes.

>>>>

We also randomly generate test scenarios under the above setting to
exam the efficiency of our approach for verifying the schedulability,
on an Intel Core 2 Quad Q9550, 2.83GHz, 4-cores machine with 8GB RAM
running 64-bit Ubuntu 15.04. Among the $50$ generated test scenarios
with $5$ tasks, we find that the execution time of the model checking
command for each scenario varies from about $300ms$ up to a timeout,
which is set to $90$ minutes. This is because the efficiency of model
checking depends on the scale of the state space. And the scale is
further positively correlated with $mn$, where $m$ is the upper bound
of $timer$ and $n$ is the number of periodic tasks. By the generated
test scenarios, it turns out that the model checking command for
schedulability in our model is able to handle scenarios, where $mn$ is
up to about $10^6$, in an acceptable period of time say $90$ minutes.
